IGRINS spectra of \name

### 2015-12-04 document/ms.tex
reformat the paper following the style from Mann et al.

@@

Figure \ref{fig:CO} shows the CO bandhead in the IGRINS spectrum of \name.

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/CO_overview} 
	\caption{CO bandhead in the IGRINS spectrum of \name.  The spectrum shows instrumental artifacts attributable to imperfectly corrected echelle blaze function.  Imperfect telluric correction is perceptible as conspicuous outliers present throughout the spectrum.  The red line is the SpeX spectrum of K0 Ib supergiant HD~44391 shown to guide the eye to the location of typical CO absorption in a stellar photosphere.  The emission in \name~  is seen \emph{in emission}.  }
	\label{fig:CO}
\end{figure*}

\acknowledgements
The authors thank Gregory N. Mace and/or Kyle Kaplan for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.

@@

\documentclass[revtex4]{emulateapj}
\usepackage[usenames,dvipsnames]{color}
\usepackage{natbib,graphicx,latexsym,lscape}

\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{url}
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\citestyle{aa}
\slugcomment{\bf November 25, 2015 draft}
\shortauthors{Gully-Santiago \emph{et al.}}
\shorttitle{Welter}

\title{Welter is an ongoing analysis of a young star in Taurus}

\author{M.~A.~Gully-Santiago}
\affil{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing, P. R. China}

\author{G. Herczeg}
\affil{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing, P. R. China}

%------------------------------------------------------------------------------------------
\section{Introduction}
%------------------------------------------------------------------------------------------

Hello world.

See \citet{2011ARA&A..49...67W} for a review about circumstellar disks.
%------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------
%Bibliography
%------------------------------------------------------------------------------------------
\bibliographystyle{apj}
\bibliography{ms}

>>>>

\subsection{Previous studies of \name}\label{sec:prev}

@@

\acknowledgements
The authors thank Gregory N. Mace for carrying out the IGRINS observations. This research has made use of NASA's Astrophysics Data System.

@@
